---
title: "SHASHIKANT DEWANGAN asignment1"
output:
  html_document: default
  pdf_document: default
---
1. For top ten parties compute the following metrics for the year 2009
 a) Total number of contestants
```{r}
library(dplyr)
parliament<- read.csv("file:///C:/Users/Administrator/Desktop/Data Visuvalizaion/datasets/parliament.csv")
top10_cont <- parliament %>%
  filter(YEAR==2009) %>% 
  group_by(PARTY) %>% 
  summarise(sum_of_contesntants=n()) %>% 
  arrange(-sum_of_contesntants)%>%
  head(10)
print(top10_cont)
```
#1-b) Total of number of winning seats

```{r}
total_win_seat=parliament %>%
  filter(YEAR==2009,Position==1) %>% 
  group_by(PARTY) %>%
  summarise(win_seats=n()) %>% 
  arrange(-win_seats) %>%
  head(10)
print(total_win_seat)
```
#1-c) Avg. %of votes
```{r}
sum_total=parliament %>% 
  filter(YEAR==2009) %>% 
  select(PARTY,VOTES) %>%
  summarise(sum_vot=sum(VOTES))

party_wise_votes=parliament %>%
  filter(YEAR==2009) %>% 
  group_by(PARTY) %>% 
  
  summarise(sum_part=sum(VOTES))


parties_year_avg <- merge(party_wise_votes,sum_total)

parties_year_avg <- parties_year_avg %>% 
  mutate(perc_avg=sum_part/sum_vot*100) %>% 
  arrange(-perc_avg) %>% 
  head(10)
print(parties_year_avg)
```
1-d) Identify top ten candidates with highest %margin of votes for the year 2009
```{r}


top_candidates <- parliament %>%
  group_by(NAME) %>%
  filter(Position == 1,
         YEAR == 2009) %>%
  summarise(total_votes = sum(VOTES)) %>%
  arrange(desc(total_votes)) %>%
  top_n(10)

second_last_candidates <- parliament %>%
  group_by(NAME) %>%
  filter(Position == 2,
         YEAR == 2009) %>%
  summarise(total_votes = sum(VOTES)) %>%
  arrange(desc(total_votes)) %>%
  top_n(10)

margin = (top_candidates$total_votes - second_last_candidates$total_votes) /
  second_last_candidates$total_votes
print(margin *100)


```
2. Identify year wise percentage of male and female candidates?
```{r}
Male_numbers=parliament %>% filter(SEX=='M') %>% group_by(YEAR) %>% summarise(male=n())

Female_numbers=parliament %>% filter(SEX=='F') %>% group_by(YEAR) %>% summarise(female=n())
total_candidate1 <- parliament %>% group_by(YEAR) %>% summarise(total=n())
male_percentage_merge <- merge(Male_numbers,total_candidate1)

MALE_PERCENTAGE=male_percentage_merge %>% mutate(male_per=male/total*100)
female_percntage_merge=merge(Female_numbers,total_candidate1)

FEMALE_PERCENTAGE=female_percntage_merge %>% mutate(female_per=female/total*100)

PERCENTAGE=merge(MALE_PERCENTAGE,FEMALE_PERCENTAGE)
print(PERCENTAGE)

```
3. Create a new column by binning the Runs column using the following ranges and plot the frequency count of ranges
0-25, 26-50, 51-75, 76-100, 100+

```{r}
library(dplyr)
library(ggplot2)
library(plotly)
setwd("C:/Users/Administrator/Desktop/Data Visuvalizaion/datasets")
odi <- read.csv("file:///C:/Users/Administrator/Desktop/Data Visuvalizaion/datasets/odi-batting.csv")

odi = odi %>% mutate(Run_bin=case_when(Runs %in% c(0:25)~c("0-25"), Runs %in% c(26:50)~c("26-50"), Runs %in% c(51:75) ~c("51-75"), Runs %in% c(76:100)~c("76-100"),Runs>100~c("100+")))

Bins_Table = odi %>% group_by(Run_bin) %>% summarise(Freq=n())
print(Bins_Table)
#plotting
ggplot(na.omit(Bins_Table),aes(x=reorder(Run_bin,-Freq),y=Freq,fill=Run_bin))+geom_bar(stat='identity')+xlab("Run Range")+ylab("Frequency Count")+scale_fill_discrete(name="RunSlots")

```
4. Consider the top ten players by total runs and compute and visualize the number of centuries across years (use facet_grid or facet_wrap)
```{r}
odi$MatchDate <- as.Date(odi$MatchDate,"%m-%d-%Y")
odi$Year <- format(odi$MatchDate,"%Y")
top_player_by_run <- odi %>% group_by(Player) %>%
  summarise(top_run=sum(Runs)) %>% 
  arrange(-top_run) %>%
  head(10)

top_player_by_run <- rbind(odi$Year,top_player_by_run)
centry_year_wise = odi %>%
  group_by(Player, Year) %>%
  filter(Player %in% top_player_by_run$Player) %>%
  summarise(cc = sum(Runs >= 100)) 
print(top_player_by_run)

g <- ggplot(data=centry_year_wise,aes(x=Year,y=cc,color=Player))+
  geom_point()+
  facet_grid(~Player)
ggplotly(g)
```
5. Create a scatter plot with the following details X axis contains number of retweets  Y axis contains number of likes Color represents device from which it was tweeted
```{r}
tweet <- read.csv("file:///C:/Users/Administrator/Desktop/Data Visuvalizaion/datasets/narendramodi_tweets.csv")
library(ggplot2)
ggplot(data=tweet,aes(x=retweets_count,y=favorite_count,color=source))+geom_point(stat = 'identity')
```


